Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-08 edubots_surveys.Rnw
fixes more typos in p20 and 21 refs#48

The surveys have the same common, initial questions for segmentation:\begin{itemize}
\item Degrees or titles where the teacher was working, either university or other tertiary education.
\item Discipline: Engineering, Social Sciences, Health and Bio, Sciences, Humanities, Other.
\item Gender: Man, Woman, Rather not say.
\item Age: 25-35, 35-45, 45-55, more than 55.
\item Experience on the job: up to 5 years, 5-15 years, 15-25 years, more than 25 years.
\item Type of degree: university, other tertiary education. This question was implicit in the first survey, since one and the other filled different forms, it was explicit in the second survey.
\end{itemize}

% Including questions in surveys
The {\bf first survey}, which focused about the use of messaging apps in class, and which tried to address mainly RQ2 and RQ3, 
% Antonio - I guess it refers to RQ3. ;)
includes the following questions:

\textit{1. Regarding the use of messaging apps in class, you prefer ...}
\begin{itemize}
\item A chat group with the students in the same course
\item Students self-organize and with the teacher not being part of any chat group
\item A chat group with the all the students and teachers of the School/High-School/Faculty
\item A chat group with all the students and teachers of the same study year
\end{itemize}

>>>>

The surveys have the same common, initial questions for segmentation:\begin{itemize}
\item Degrees or titles where the teacher was working, either university or other tertiary education.
\item Discipline: Engineering, Social Sciences, Health and Bio, Sciences, Humanities, Other.
\item Gender: Man, Woman, Rather not say.
\item Age: 25-35, 35-45, 45-55, more than 55.
\item Experience on the job: up to 5 years, 5-15 years, 15-25 years, more than 25 years.
\textcolor{blue}{
\item Type of degree: university, other tertiary education. This question was implicit in the first survey: there were two different versions of the survey. However, it was and explicit question in the second survey.}
\end{itemize}

% Including questions in surveys
The {\bf first survey}, which \textcolor{blue}{focused on} the use of messaging apps in class, and which tried to address mainly RQ2 and RQ3, 
% Antonio - I guess it refers to RQ3. ;)
includes the following questions:

\textit{1. Regarding the use of messaging apps in class, you prefer ...}
\begin{itemize}
\item A chat group with the students in the same course
\item Students self-organize and with the teacher not being part of any chat group
\textcolor{blue}{
\item A chat group with all the students and teachers of the School/High-School/Faculty
}
\item A chat group with all the students and teachers of the same study year
\end{itemize}
